### 2021-06-07 papers/thesis/full/ch2-spherical-harmonics/spherical-harmonics.tex
New images for SH plots (removing shading/shadowing)

\begin{figure}[t]
	\centering % <-- added
	\centerline{\includegraphics[scale=0.5]{heat-eqn-alpha-0p0238-dt=0p01-nsteps=100}}
	\caption{Four snapshots of the solution $u$ of the heat equation with $\alpha = 1/42$ and a step size of $\Delta t = 0.01$, solved using the BDF2 timestepping method. Top Left: Initial conditions (0 timesteps). Top Right: After 25 timesteps. Bottom Left: After 50 timesteps. Bottom Right: After 75 timesteps.}
	\label{fig:heateqn}
\end{figure}

@@

\begin{figure}[t]
	\centering % <-- added
	\centerline{\includegraphics[scale=0.5]{linear-swe-H=1-dt=0p01-nsteps=100-arrows}}
	\caption{Four snapshots of the solution for the height $h$ (surface colour) and the wave velocity $u$ (red arrows) of the linearised shallow water equations with $\rotrate = \calH = 1$ and a step size of $\Delta t = 0.01$, solved using the backwards Euler timestepping method (BDF1). The initial conditions are given in \bsrefeqn{eqn:sweics}. Top Left: Initial conditions (0 timesteps). Top Right: After 50 timesteps. Bottom Left: After 75 timesteps. Bottom Right: After 100 timesteps.}
	\label{fig:swe}
\end{figure}

>>>>

\begin{figure}[t]
	\centering % <-- added
	\centerline{\includegraphics[scale=0.5]{heat-eqn-alpha-0p0238-dt=0p01-nsteps=100-2}}
	\caption{Four snapshots of the solution $u$ of the heat equation with $\alpha = 1/42$ and a step size of $\Delta t = 0.01$, solved using the BDF2 timestepping method. Top Left: Initial conditions (0 timesteps). Top Right: After 25 timesteps. Bottom Left: After 50 timesteps. Bottom Right: After 75 timesteps.}
	\label{fig:heateqn}
\end{figure}

@@

\begin{figure}[t]
	\centering % <-- added
	\centerline{\includegraphics[scale=0.5]{linear-swe-H=1-dt=0p01-nsteps=100-arrows-2}}
	\caption{Four snapshots of the solution for the height $h$ (surface colour) and the wave velocity $u$ (red arrows) of the linearised shallow water equations with $\rotrate = \calH = 1$ and a step size of $\Delta t = 0.01$, solved using the backwards Euler timestepping method (BDF1). The initial conditions are given in \bsrefeqn{eqn:sweics}. Top Left: Initial conditions (0 timesteps). Top Right: After 50 timesteps. Bottom Left: After 75 timesteps. Bottom Right: After 100 timesteps.}
	\label{fig:swe}
\end{figure}
